\documentclass[10pt, letterpaper]{fulldeps}

\RequirePackage{fix-cm}
\usepackage[fontsize=10.5pt]{scrextend}
%
% Preamble
%
\usepackage{graphicx}

\setlength{\columnseprule}{0.2pt}

%
% Document Environment
%
\begin{document}

%
% Name
%
\textbf{\fontsize{25}{25}\selectfont Pratyush Das}
\vspace{0.4cm}

%
% Personal Entries
%
\vspace{-45pt} \begin{spacing}{1}
\PersonalEntry{\textbullet{} Phone}{(+91) 9051603323}
\PersonalEntry{\textbullet{} Email}{\href{mailto:das160@purdue.edu}{das160@purdue.edu}}
\PersonalEntry{\textbullet{} GitHub}{\urlstyle{same}\url{https://github.com/reikdas}}
\end{spacing}
\vspace{-13pt}

%
% Education
%
\vspace{10pt}
\Section{Education}
\vspace{-4pt}
\EducationEntry{\textbf{Purdue University}}{2021 -}{PhD in Computer Science (Advisor - Tiark Rompf)}{}\\
\EducationEntry{\textbf{Institute of Engineering \& Management, Kolkata (MAKAUT)}}{2017 - 2021}{Bachelor of Technology in Computer Science and Engineering. CGPA: 8.89/10}{}
%\EducationEntry{\textbf{Don Bosco School, Park Circus, Kolkata}}{2016}{High School (Council For The Indian School Certificate Examinations)}{}
\vspace{-10pt}

\Section{Teaching Experience}
\vspace{-4pt}
\ExperienceEntry{\textbf{CS 240: Programming in C}}{August, 2021 - December, 2021}{Purdue University}{Teaching Assistant for 250 students}{}\vspace{-23pt}

%
% Professional Experience
%
\Section{Work Experience}
\vspace{-4pt}
\ExperienceEntry{\textbf{Google Summer of Code - Student}}{June, 2021 - August, 2021}{The LLVM Compiler Infrastructure Organization}{Supervisors - William Moses (MIT), Dr. Johannes Doerfert (Argonne National Laboratory)}{
    \vspace{-10pt}
    \begin{tightitemize}
    \item \href{https://enzyme.mit.edu/}{Enzyme}: LLVM Pass to perform automatic differentiation of statically analyzable LLVM IR
        \subitem - Integrated custom derivatives of BLAS functions into Enzyme.
        \subitem - Wrote an LLVM pass to inline function definitions from bitcode files into LLVM IR.
    \end{tightitemize}
}\vspace{4pt}\\
\ExperienceEntry{\textbf{{\href{https://iris-hep.org/}{IRIS-HEP}} - Fellow}}{June, 2020 - September, 2020}{}{Supervisor - Dr. Jim Pivarski (Princeton University)}{
	\vspace{-10pt}
	\begin{tightitemize}
    \item \href{https://github.com/scikit-hep/awkward-1.0}{Awkward Array}: Library for nested, variable-sized data using NumPy-like idioms
        \subitem - Created a source to source compiler to generate equivalent Python for a subset of C++.
        \subitem - Created a property based testing framework.
        \subitem - Created a source to source compiler to generate equivalent parallel CUDA from specification (Python and type info).
	\end{tightitemize}
} \vspace{4pt}\\
\ExperienceEntry{\textbf{{\href{https://iris-hep.org/}{IRIS-HEP}} - Fellow}}{June, 2019 - September, 2019}{Location: Fermi National Accelerator Laboratory, USA - LHC Physics Centre}{Supervisor - Dr. Jim Pivarski (Princeton University)}{
	\vspace{-10pt}
	\begin{tightitemize}
    \item \href{https://github.com/scikit-hep/uproot3.git}{Uproot}: Python implementation of ROOT I/O, an open source file format storing over an exabyte of HEP data
        \subitem - Completed ROOT file writing interface by adding functionality to write ROOT files with TTrees.
        \subitem - Uproot has become one of the most widely used Physics libraries (50K+ downloads).
	\end{tightitemize}
} \vspace{4pt}\\
\ExperienceEntry{\textbf{{\href{http://diana-hep.org/}{DIANA-HEP}} - Fellow}}{June, 2018 - September, 2018}{Location: Fermi National Accelerator Laboratory, USA - LHC Physics Centre}{Supervisor - Dr. Jim Pivarski (Princeton University)}{
      \vspace{-10pt}
      \begin{tightitemize}
      \item \href{https://github.com/scikit-hep/uproot3.git}{Uproot}
              \subitem - Co-developed the Uproot library with Jim Pivarski; authored the ROOT file writing interface.
            \subitem - Examined ROOT serialization of objects and added functionality to write ROOT files with object strings and histograms.
      \end{tightitemize}
}
\vspace{-3pt}

\Section{Volunteer Research Experience}
\vspace{-4pt}
\ExperienceEntry{\textit{Supervisor} - Dr. Vassil Vassilev (Princeton University)}{November, 2019 - May, 2021}{}{\textit{Collaborations}: \href{iris-hep.org}{IRIS-HEP}, CERN ROOT Team, \href{https://compiler-research.org/}{Compiler Research group}}{
    \vspace{-10pt}
    \begin{tightitemize}
    \item \textbf{\href{https://github.com/root-project/root}{ROOT}}: An open-source data analysis framework storing over an exabyte of data
        \subitem - Created new unit testing library, ROOTUnitTestSupport
        \subitem - Some rootcling improvements
        \subitem - Fixed packaging for macOS
        \subitem - Backported several Clang patches from upstream LLVM/Clang
    \item \textbf{\href{https://github.com/root-project/cling}{Cling}}: Interactive C++ interpreter built on top of Clang
        \subitem - Configured installer to build using LLVM binary
        \subitem - Fixed CI and moved it from Travis to GitHub Actions
        \subitem - Maintained cpt.py installer and packager
    \item \textbf{\href{https://clang.llvm.org/}{Clang}}: C language family frontend for LLVM
        \subitem - Several patches to print type information of C++ template arguments
    \item \textbf{\href{https://github.com/vgvassilev/clad}{Clad}}: Clang plugin for automatic differentiation
        \subitem - Moved CI from Travis to Github Actions.
    \end{tightitemize}
}\vspace{4pt}\\
\ExperienceEntry{\textit{Supervisor} - Dr. Jim Pivarski (Princeton University)}{January, 2021 - February, 2021}{}{\textit{Collaborations}: \href{iris-hep.org}{IRIS-HEP}}{
    \vspace{-10pt}
    \begin{tightitemize}
    \item \textbf{\href{https://github.com/scikit-hep/awkward-1.0}{Awkward Array}}
        \subitem - Created a parser for Awkward Array's type system
    \end{tightitemize}
} \vspace{-1pt}\\
\ExperienceEntry{\textit{Supervisors} - Dr. Jim Pivarski (Princeton University), Dr. Viktor Khristenko (CERN)}{June, 2017 - August, 2017}{}{\textit{Collaborations}: CERN CMS Big Data Project, {\href{diana-hep.org}{DIANA-HEP}}}{
    \vspace{-10pt}
    \begin{tightitemize}
    \item \textbf{\href{https://github.com/diana-hep/spark-root}{spark-root}} - Apache Spark datasource for ROOT
        	\subitem - Separated spark bindings from TTree reading code.
        \item \textbf{\href{https://github.com/diana-hep/spark-root}{root4j}} - Java implementation of ROOT file reader
        	\subitem - Optimized codebase to facilitate interoperability
    \end{tightitemize}
}
\vspace{-3pt}

%
% Programming Skills
%
\Section{Programming Languages and Tools}
\vspace{-4pt}
\textbf{Experienced:} Python, C, CUDA, *nix

\textbf{Familiar:} C++, Java, Scala, ROOT
\vspace{-6pt}

%
% Workshops and Summer Schools
%
\Section{Summer Schools}
\vspace{-4pt}
\EducationEntry{\textbf{{\href{https://www.cs.uoregon.edu/research/summerschool/summer21/index.php}{Oregon Programming Languages Summer School}}}}{2021}{University of Oregon}{}\\
\EducationEntry{\textbf{{\href{https://codas-hep.org/}{Computational and Data Science for High Energy Physics (CoDaS-HEP)}}}}{2019}{Princeton University}{}\\
\vspace{-15pt}
\begin{tightitemize}
\item Interviewed - \textit{\href{https://www.princeton.edu/news/2019/08/19/princeton-leads-efforts-develop-national-data-training-framework-high-energy}{Princeton University News}}
\end{tightitemize}
%\vspace{2pt}
%\EducationEntry{\textbf{{\href{https://indico.cern.ch/event/822126/}{Fast Machine Learning Workshop}}}}{2019}{Fermi National Accelerator Laboratory}{}\\
%\vspace{-22pt}
\vspace{-5pt}

%
% Publications
%
\Section{Publications}
\small{\begin{tightitemize}
    \item J.Pivarski, I.Osborne, {\textbf{P.Das}}, D.Lange, P.Elmer, {\href{https://www.epj-conferences.org/articles/epjconf/abs/2021/05/epjconf_chep2021_03002/epjconf_chep2021_03002.html}{``AwkwardForth: accelerating Uproot with an internal DSL''}}, 25th International Conference on Computing in High-Energy and Nuclear Physics (vCHEP, 2021), DOI: 10.1051/epjconf/202125103002. \hfill{2021}
    \item J.Pivarski, I.Osborne, {\textbf{P.Das}}, A.Biswas, P.Elmer, {\href{http://conference.scipy.org/proceedings/scipy2020/jim_pivarski.html}{``Awkward Array: JSON-like data, NumPy-like idioms''}}, Proceedings of the 19th Python in Science Conference (SciPy USA, 2020), Pages 68-74, DOI: 10.25080/Majora-342d178e-00b. \hfill{2020}
    \item E.Rodrigues, et al., {\href{https://www.epj-conferences.org/articles/epjconf/abs/2020/21/epjconf_chep2020_06028/epjconf_chep2020_06028.html}{``The Scikit HEP Project - overview and prospects``}}, Proceedings of the 24th International Conference on Computing in High Energy and Nuclear Physics (CHEP 2019), DOI: 10.1051/epjconf/202024506028.  \hfill{2020}
    \item N.Saha, {\textbf{P.Das}}, H.N.Saha, {\href{https://www.inderscienceonline.com/doi/abs/10.1504/IJAPR.2018.094819}{``Authorship Attribution of Short Texts using a Multi Layer Perceptron''}}, International Journal of Applied Pattern Recognition, 2018 Vol. 5 No. 3, Pages 251-259, DOI: 10.1504/IJAPR.2018.10016100. \hfill{2018}
\end{tightitemize}}

%
% Presentations
%
\Section{Invited talks at Conferences}
\vspace{-4pt}
\PresentationEntry{\textbullet{} GSoC Experience - Enzyme}{\small{-{LLVM Developers' Meeting} (Remote)}} \hfill{2021}\\
\PresentationEntry{\textbullet{} {\href{https://youtu.be/jClVsR6XfdI}{Python in High Energy Physics}}}{\small{-{\href{https://us.pycon.org/2020/}{PyCon USA}} (Remote)}} \hfill{2020}\\
\PresentationEntry{\textbullet{} {\href{https://static.fossee.in/scipy2019/SciPyTalks/SciPyIndia2019_S008_Python_in_High_Energy_Physics_20191130.mp4}{Python in High Energy Physics}}}{\small{-{\href{https://scipy.in/2019}{SciPy India}} (Indian Institute of Technology, Bombay)}} \hfill{2019}\\
%\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/773049/contributions/3476182/attachments/1938227/3213768/EduardoRodrigues_2019-11-05_CHEP2019Adelaide.pdf}{The Scikit-HEP Project: Overview and Prospects} - \underline{Eduardo Rodrigues} et al.}}{\small{-{\href{http://chep2019.org/}{24th International Conference on Computing in High Energy and Nuclear Physics}} (University of Adelaide)}} \hfill{2019}\\
\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/833895/contributions/3577892/attachments/1927752/3191883/uproot-pyhep.pdf}{Writing files with uproot}}}{\small{-{\href{https://indico.cern.ch/event/833895/}{PyHEP}} (Abington, UK)}} \hfill{2019}\\
\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/697389/contributions/3102807/attachments/1713054/2762448/Writing_files_with_uproot.pdf}{Writing files with uproot}}}{\small{-{\href{https://indico.cern.ch/event/697389/}{ROOT Users' Workshop}} (Academy of Sciences and Arts of Bosnia and Herzegovina)}} \hfill{2018}\\
\vspace{-15pt}

\Section{Invited talks at External Research Group Meetings}
\vspace{-4pt}
\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/946427/}{Language Transformations for the Awkward Array library}}}{\small{-{\href{https://indico.cern.ch/event/946427/contributions/3976986/attachments/2094014/3519161/IRIS-HEP-Fellow-Awkward.pdf}{IRIS-HEP Fellow Presentations}} (Remote)}} \hfill{2020}\\
\PresentationEntry{\textbullet{} CUDA backend for the Awkward Array project}{-Princeton University Liberty Research Group Meeting (Remote)} \hfill{2020}\\
%\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/913583/contributions/3841826/attachments/2027488/3392299/PR5297_--_Testing_Facilities.pdf}{PR 5297: Testing Facilities} - \underline{Vassil Vassilev}, Pratyush Das}}{\small{-{\href{https://indico.cern.ch/event/913583/}{ROOT Team Meeting}} (Remote)}} \hfill{2020}\\
\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/840667/contributions/3527109/attachments/1908764/3153297/uproot-irisfellow-final.pdf}{Writing TTrees with uproot}}}{\small{-{\href{https://indico.cern.ch/event/840667/}{IRIS-HEP Topical Meeting: Summer student project presentations}} (Remote)}} \hfill{2019}\\
\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/754335/contributions/3166239/attachments/1734208/2804184/Writing_files_with_uproot_-_DIANA_HEP.pdf}{Writing files with uproot}}}{\small{-{\href{https://indico.cern.ch/event/754335/}{DIANA Meeting: Updates on ROOT I/O}} (Remote)}} \hfill{2018}\\
\PresentationEntry{\textbullet{} {\href{https://indico.cern.ch/event/658754/contributions/2685907/attachments/1506368/2347492/Refactoring_code_from_spark-root_to_root4j.pdf}{Separation of Concerns - Refactoring code between ROOT4J and Spark-Root}}}{\small{-{\href{https://indico.cern.ch/event/655833/}{DIANA Meeting: Student Projects}} (Remote)}; {\href{https://indico.cern.ch/event/658754/}{CMS Big Data Science Projects}} (Remote)}\hfill{2017}\\
\vspace{-15pt}

%
% Patents
%
%\Section{Patents}
%\small{\begin{tightitemize}
%    \item Autonomous navigation system for driverless cars, Application no. - 201831024950. \hfill{2018}
%\end{tightitemize}}

\newpage{}
%
% Achievements
%
\Section{Achievements}
\begin{tightitemize}
    \item PurPL funding to attend OOPSLA, 2021. \hfill{2021}
    \item Awarded the Director's Award for Best Scientific Mind by the Institute of Engineering \& Management, Kolkata. \hfill{2021}
    \item Awarded PLMW scholarship to attend POPL, 2021. \hfill{2021}
    \item Awarded PLMW scholarship to attend ICFP, 2020. \hfill{2020}
    \item Awarded PLMW scholarship to attend PLDI, 2020. \hfill{2020}
    \item Awarded the IRIS-HEP undergraduate fellowship by Princeton University. \hfill{2020}
    \item Awarded travel grant to speak at PyCon USA, 2020 in Pittsburgh, USA. \hfill{2020}
    \item Awarded PLMW scholarship to travel to and attend POPL, 2020 in New Orleans, USA. \hfill{2020}
    \item Awarded travel grant to attend CoDaS-HEP summer school at Princeton University. \hfill{2019}
    \item Awarded the IRIS-HEP undergraduate fellowship by Princeton University. \hfill{2019}
    \item Awarded travel grant to speak at ROOT Users' Workshop, 2018 in Sarajevo, Bosnia and Herzegovina. \hfill{2018}
	\item Awarded the DIANA-HEP undergraduate fellowship by Princeton University. \hfill{2018}
\end{tightitemize}

\Section{Relevant Coursework}
\begin{tightitemize}
\item Advanced Topics in Compilers (Purdue CS592-ATC)
\item Software Engineering (IEM CS701, IEM CS791)
\item Compiler Design (IEM CS702)
\item Artificial Intelligence (IEM CS703C, IEM CS793C)
\item Database Management System (IEM CS601, IEM CS691)
\item Operating System (IEM CS603, IEM CS693)
\item Operations Research (IEM CS605A)
\item Design and Analysis of Algorithms (IEM CS501, IEM CS591)
\item Discrete Mathematics (IEM CS502)
\item Object Oriented Programming (IEM CS504D, IEM CS594D)
\item Numerical Methods (IEM MCS401, IEM MCS491)
\item Mathematics (IEM M401)
\item Formal Languages and Automata Theory (IEM CS403)
\item Computer Architecture (IEM CS403, IEM CS493)
\item Basic Computation and Principles of Computer Programming (IEM CS291)
\end{tightitemize}
\end{document}
